---
title: "Bootstrap Components"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bootstrap Components}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css echo=FALSE}
/* override pkgdown.css */
.warning {
  color: #333;
  font-weight: normal;
}
```


[Bootstrap](https://getbootstrap.com/) is a popular HTML, CSS and JS framework.  It has made its way into the world of R in many forms, perhaps most notably via [R Markdown](https://rmarkdown.rstudio.com/) and [R Shiny](https://shiny.rstudio.com/).  `mayotheme` contains a customized Bootstrap theme, making it easy to integrate into your own documents and applications.  The preview below is based on the work of [Bootswatch](https://bootswatch.com/).  

These components can be used whether you are creating a static report, interactive documents, or a full application.  For more details on how, please reference the Bootsrap and R Shiny documentation.  

```{r eval=FALSE, echo=FALSE}
htmltools::includeHTML("bootstrap_demo.html")
```



